Poincar\'e--Friedrichs constants over domains with shellable triangulations

### 2024-06-28 draft.tex
additional work on potentials

@@

\end{document}

>>>>

\begin{lemma}
    Let $\Omega \subseteq \bbR^{n}$. There exists a bounded mapping 
    \begin{align*}
     \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
    \end{align*}
    such that 
    \begin{align*}
        \| u \|_{L^{p}} \leq n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} D \| u \|_{L^{p}(\Omega)}
    \end{align*}
    and such that $\cartan \Bogov_{\ell} u = u$ for all $u \in \cartan \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$.
\end{lemma}

\begin{lemma}
    Let $\Omega \subseteq \bbR^{n}$. There exists a bounded mapping 
    \begin{align*}
     \Bogov_{\ell} : L^{p}(\Omega,\Alt^{\ell}) \rightarrow \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})
    \end{align*}
    such that 
    \begin{align*}
        \| u \|_{L^{p}} \leq n A(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} D \| u \|_{L^{p}(\Omega)}
    \end{align*}
    and such that $\cartan \Bogov_{\ell} u = u$ for all $u \in \cartan \bfW^{p}_{0}(\Omega,\Alt^{\ell-1})$.
\end{lemma}

There exists a sequence $u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell})$ that converges to $u$ in $W^{p}(\Omega,\Alt^{\ell})$
and which satisfies $\cartan u_{i} = 0$. Let $w \in L^{p}(\Omega,\Alt^{\ell-1})$ be the limit of $\Poinc_{\ell} u_{i}$.
We know that $\Poinc_{\ell} u_{i} \in C^{\infty}(\overline\Omega,\Alt^{\ell-1})$. 
Given any $v \in C^{\infty}_{c}(\Omega,\Alt^{n-\ell-1})$, we verify 
\begin{align*}
    \int_{\Omega} w \wedge \cartan v
    &=
    \lim_{i} \int_{\Omega} \Poinc_{\ell} u_{i} \wedge \cartan v
    \\&=
    \lim_{i} \int_{\Omega} \cartan \Poinc_{\ell} u_{i} \wedge v
    \\&=
    \lim_{i} \int_{\Omega} u_{i} \wedge v
    =
    \int_{\Omega} u \wedge v
    .
\end{align*}
That means $w \in W^{p}(\Omega,\Alt^{\ell-1})$ with $\cartan w = u$.

@@

    Bogovskii was the first establish the 
    on whose work the following presentation is based. 
    In contrast to the aforementioned reference, the goal of our discussion is more modest:
    we merely need them over convex sets and are only interested in their operator norms between Lebesgue spaces.
    However, we derive explicit bounds for the operator norms, which are of independent interest.

    It can be identified as a formal adjoint to the Poincar\'e operator in exterior calculus. 
    The Bogovski\u{\i}-type potential operator first appeared for the mathematical discussion of hydrodynamical models~\cite{bogovskii1979solution} and has since been extended to exterior calculus. 
    The regularized Bogovski\u{\i} potential operator was studied extensively by Costabel and McIntosh.
    These operators are defined over sets star-shaped with respect to a ball.

    The generalization to differential forms has been discussed extensively by Costabel and McIntosh~\cite{costabel2010bogovskiui},
    on whose work the following presentation is based. 
    In contrast to the aforementioned reference, the goal of our discussion is more modest:
    we merely need them over convex sets and are only interested in their operator norms between Lebesgue spaces.
    However, we derive explicit bounds for the operator norms, which are of independent interest.

    Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis. However, no operator norm estimates are given in the literature, to the best of our best knowledge.
    We study a variation of this potential operator over convex sets.
    We simply use a constant averaging over the entire domain. 
    While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
    this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms. 
\end{document}
